---
title: "R Notebook"
output: html_notebook
---

# Section 4.6 Choosing Final Tuning Parameters

```{r}
library(caret)
data(GermanCredit)
```

First, remove near-zero variance predictors then get rid of a few predictors that duplicate values. For example, there are two possible values for the housing variable: "Rent", "Own" and "ForFree". So that we don't have linear dependencies, we get rid of one of the levels (e.g. "ForFree")

```{r}
GermanCredit <- GermanCredit[, -nearZeroVar(GermanCredit)]
GermanCredit$CheckingAccountStatus.lt.0 <- NULL
GermanCredit$SavingsAccountBonds.lt.100 <- NULL
GermanCredit$EmploymentDuration.lt.1 <- NULL
GermanCredit$EmploymentDuration.Unemployed <- NULL
GermanCredit$Personal.Male.Married.Widowed <- NULL
GermanCredit$Property.Unknown <- NULL
GermanCredit$Housing.ForFree <- NULL
```


Split the data into training (80%) and test sets (20%)
```{r}
set.seed(100)
inTrain <- createDataPartition(GermanCredit$Class, p = .8)[[1]]
GermanCreditTrain <- GermanCredit[ inTrain, ]
GermanCreditTest  <- GermanCredit[-inTrain, ]
```


The model fitting code shown in the computing section is fairly simplistic.  For the text we estimate the tuning parameter grid up-front and pass it in explicitly. This generally is not needed, but was used here so that we could trim the cost values to a presentable range and to re-use later with different resampling methods.

```{r}
library(kernlab)
set.seed(231)
sigDist <- sigest(Class ~ ., data = GermanCreditTrain, frac = 1)
svmTuneGrid <- data.frame(sigma = as.vector(sigDist)[1], C = 2^(-2:7)) 
```
**Optional**: parallel processing can be used via the 'do' packages, such as doMC, doMPI etc. We used doMC (not on Windows) to speed up the computations.

**WARNING**: Be aware of how much memory is needed to parallel process. It can very quickly overwhelm the available hardware. We estimate the memory usage (VSIZE = total memory size) to be 2566M/core.


```{r}
library(doMC)
registerDoMC(4)

set.seed(1056)
svmFit <- train(Class ~ .,
                data = GermanCreditTrain,
                method = "svmRadial",
                preProc = c("center", "scale"),
                tuneGrid = svmTuneGrid,
                trControl = trainControl(method = "repeatedcv", 
                                         repeats = 5,
                                         classProbs = TRUE))
```

**classProbs = TRUE** was added since the text was written. 

Print the results
```{r}
svmFit
```

A line plot of the average performance. The 'scales' argument is actually an argument to xyplot that converts the x-axis to log-2 units.

```{r}
plot(svmFit, scales = list(x = list(log = 2)))
```

Test set predictions
```{r}
predictedClasses <- predict(svmFit, GermanCreditTest)
str(predictedClasses)
```
Use the "type" option to get class probabilities

```{r}
predictedProbs <- predict(svmFit, newdata = GermanCreditTest, type = "prob")
head(predictedProbs)
```

Fit the same model using different resampling methods. The main syntax change is the control object.
```{r}
set.seed(1056)
svmFit10CV <- train(Class ~ .,
                    data = GermanCreditTrain,
                    method = "svmRadial",
                    preProc = c("center", "scale"),
                    tuneGrid = svmTuneGrid,
                    trControl = trainControl(method = "cv", number = 10))
svmFit10CV
```

```{r}
set.seed(1056)
svmFitLOO <- train(Class ~ .,
                   data = GermanCreditTrain,
                   method = "svmRadial",
                   preProc = c("center", "scale"),
                   tuneGrid = svmTuneGrid,
                   trControl = trainControl(method = "LOOCV"),verboseIter= TRUE)
svmFitLOO
```


```{r}
set.seed(1056)
svmFitLGO <- train(Class ~ .,
                   data = GermanCreditTrain,
                   method = "svmRadial",
                   preProc = c("center", "scale"),
                   tuneGrid = svmTuneGrid,
                   trControl = trainControl(method = "LGOCV", 
                                            number = 50, 
                                            p = .8))
svmFitLGO
```

```{r}
set.seed(1056)
svmFitBoot <- train(Class ~ .,
                    data = GermanCreditTrain,
                    method = "svmRadial",
                    preProc = c("center", "scale"),
                    tuneGrid = svmTuneGrid,
                    trControl = trainControl(method = "boot", number = 50))
svmFitBoot
```

```{r}
set.seed(1056)
svmFitBoot632 <- train(Class ~ .,
                       data = GermanCreditTrain,
                       method = "svmRadial",
                       preProc = c("center", "scale"),
                       tuneGrid = svmTuneGrid,
                       trControl = trainControl(method = "boot632", 
                                                number = 50))
svmFitBoot632
```







Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
